Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-23 paper.tex

\author{
  \authorname{Anon McAnon{\sup{1}}}
  \affiliation{\sup{1}Anon University of Anon, Anonville, Anonistan}
  \email{anon.anon@anon.com}
%\affiliation{\sup{1}Lincoln Centre for Autonomous Systems (L-CAS), University of Lincoln, Lincoln, UK}
%\email{jlock@lincoln.ac.uk}
}

@@

In this case, the reference signal, $r$, is the object the user wishes to capture with the smartphone's camera. The goal of the control block, $K$, is to generate human interpretable instructions, $u$, to guide the user towards the target object. The process to be controlled involves a human, $H$, who interprets the instruction and executes a physical action, $u^*$, to actually manipulates the smartphone's camera, $P$. A new observation, $y$, with the latter is then fed back to the loop and the error signal, $e$, is updated accordingly.

@@

This section describe the actual implementation details of the MDP for active object search, including training and software deployment on our smartphone device.

@@

\noindent A policy that defines the optimal action for an agent to take for any given state is generated through a training process that involves letting the agent explore the entire state-space and iteratively improve its decision function, i.e.\ policy, in order to reach the target state in a way that maximises its cumulative reward. This method, called Q-learning~\cite{Watkins1992}, does not require a model of the agent's environment during training.

@@

The lack of absolute spatial information in the OpenImage dataset generates ambiguities, which makes it hard for the model to converge to a single, optimal solution. We therefore could not use the popular value iteration algorithm~\cite{bellman1957markovian} and opted for the state-action-reward-state-action (SARSA) algorithm~\cite{rummery1994line} instead. SARSA is an on-policy algorithm that allows us to control the level of exploration vs.\ exploitation that makes it easier to find a solution, although this is not guaranteed to be optimal.

@@

We incorporated the trained MDP model and policies into an Android app (see Figure~\ref{fig:system-screenshot} for a screenshot). This app is responsible for generating the guidance instructions and tracking the agent and sensor ($K$ and $P$ blocks in Figure~\ref{fig:control-loop}) throughout a search session. Tracking the agent's pose allows the app to infer the current state and look up the optimal action to take.

@@

The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes. In this setup, the policy action is interpreted by the app and a new search waypoint is generated in the centre of the cell specified by the action, e.g.\ an `$UP$' action will generate a waypoint one grid cell up from where the user is currently pointing the camera. The app's guidance system then uses the new waypoint's location to provide the user with guidance instructions. The grid is generated at the app's start-up and remains constant throughout the app's lifetime. The policy actions, and waypoints by extension, are given in relative to the user's current viewing pan/tilt position. The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.

@@

The app was developed on and experimented with an Asus ZenPhone AR running Android version 7.0 with Google's augmented reality toolkit (ARCore) enabled for measurement and device tracking. No hardware or software modifications were required.

>>>>

\author{
  \authorname{~}%Anon McAnon{\sup{1}}}
  \affiliation{~}%\sup{1}Anon University of Anon, Anonville, Anonistan}
  \email{~}%anon.anon@anon.com}
%\affiliation{\sup{1}Lincoln Centre for Autonomous Systems (L-CAS), University of Lincoln, Lincoln, UK}
%\email{jlock@lincoln.ac.uk}
}

@@

In this case, the reference signal, $r$, is the object the user wishes to capture with the smartphone's camera. The goal of the control block, $K$, is to generate human interpretable instructions, $u$, to guide the user towards the target object. The process to be controlled involves a human, $H$, who interprets the instruction and executes a physical action, $u^*$, to actually manipulate the smartphone's camera, $P$. A new observation, $y$, with the latter is then fed back to the loop and the error signal, $e$, is updated accordingly.

@@

This section describe the actual implementation details of the MDP for active object search, including initial training and software deployment on our smartphone device.

@@

\noindent A policy that defines the optimal action for an agent to take for any given state is generated through a training process that involves letting the agent explore the entire state-space and iteratively improve its decision function, i.e.\ policy, in order to reach the target state in a way that maximises its cumulative reward. This method, called Q-learning~\cite{Watkins1992}, does not require a model of the agent's environment during training, allowing the policy to be used in many different scenarios.

@@

The lack of absolute spatial information in the OpenImage dataset generates ambiguities, which makes it hard for the model to converge to a single, optimal solution. We therefore opted to use the more conservative state-action-reward-state-action (SARSA) algorithm~\cite{rummery1994line}. SARSA is an on-policy algorithm that allows us to control the level of exploration vs.\ exploitation that makes it easier to find a solution, although this is not guaranteed to be optimal.

@@

We incorporated the trained MDP-based controller into an app (see Figure~\ref{fig:system-screenshot}) for an Asus ZenPhone AR smartphone, running Android 7.0, with the Google's augmented reality toolkit (ARCore), which provides the necessary 3D pose of the device. No further software or hardware modifications were required. This app is responsible for generating the guidance instructions and tracking the camera sensor ($K$ and $P$ blocks in Figure~\ref{fig:control-loop}) throughout a search session. Tracking the camera's pose allows the app to infer the current state and choose the optimal action to take next.

@@

The app uses a 6$\times$6 discretised and wrapped radial grid to simplify the tracking and waypoint generation processes. A policy action is converted by the app into a new search waypoint centred on a cell of the radial grid, e.g.\ an `$UP$' action will generate a waypoint one grid cell above the current the camera's orientation. Note that this cell is not part of the MDP' state: this radial grid is only used to discretised the pan-tilt movements of the camera and to guarantee a minimum angular variations between subsequent actions. The app's guidance system then uses the new waypoint's location to provide the user with guidance instructions. The grid is generated at the app's start-up and remains constant throughout the app's lifetime. The policy actions, and waypoints by extension, are given in relative to the user's current viewing pan/tilt position. The grid spans \SI{120}{\degree} in both the pan and tilt dimensions, giving a resolution of \SI{20}{\degree} per grid cell.

@@
